%کلمات کلیدی انگلیسی
\latinkeywords{Internet of Things, Real-Time Tracking System, SIM808, GPS, GSM}
%چکیده انگلیسی

\en-abstract{
	In the science of information technology, the concept of the Internet of objects refers to objects with a specific identity that have a unique identifier and the ability to transfer data to the network without the need for interaction and human intervention. In fact, its main purpose is to intelligent objects and provide a way through which objects can send and receive information with each other.\\
	In recents years, the technology of the Internet of Things has grown dramatically and has been able to meet various and complex needs in various fields. One of the Internet uses of objects is the tracking of moving objects that can be used in various areas, such as security, monitoring, transport, and so on.
	The positioning and tracking system offers the possibility of providing reliable solutions for the safety of individuals and vehicles, and also has a significant impact on the quality of the monitoring and management of transport fleets, the movement of vehicles, people (children and the elderly), or Each movable object has another. It is actually a technology tracking system that allows you to accurately locate and trace individuals, vehicles, or any other moving object using a variety of methods, such as the Global Positioning System.\\	
	This project presents the development of the remote vehicle
	tracking system which integrates the Global System for Mobile
	Communications (GSM) Modem and Google Map. we plan to implement a system that can be used to determine the precise position, direction, and locations of any moving object at any time.\\ In this system, each object is equipped with one that receives its location every two minutes from the satellite and sends it to the software servers via the modem of the GPS module. After downloading the software, the software servers analyze them as GSM. In this part of the project, a web application will be developed to process and sent information and then store it in a database, and finally convert the stored information to be displayed to users. This way, you can see the speed, the path, and the location of the object on the map.
}
%%%%%%%%%%%%%%%%%%%%% کدهای زیر را تغییر ندهید.

\newpage
\thispagestyle{empty}
\begin{latin}
\section*{\LARGE\centering Abstract}

\een-abstract

\vspace*{.5cm}
{\large\textbf{Key Words:}}\par
\vspace*{.5cm}
\elatinkeywords
\end{latin}