\vspace{2in}
\begin{abstract}
	In recent years, IoT technology has grown significantly and has been able to meet diverse and complex needs in various fields. One of the applications of the Internet of Things is real-time tracking. The positioning and tracking system has provided reliable solutions to ensure the safety of people and vehicles, and also has a significant impact on optimizing the quality of monitoring.  
	This system can be used for a broad range of applications such as traffic management and vehicle tracking/anti-theft system, and finally, traffic routing and navigation.  it can be applied in many business cases, like public transportation, so passengers can track their buses and trains by following the vehicle account on social networks.\\
	In this project, a system was developed to accurately determine the location, direction of movement, and speed of moving objects at any given time using SIM808 Module. In this system, each object is equipped with a GPS (Global Positioning System) module that receives its location every two minutes from the satellite and sends it to the software servers via the GSM modem. Software servers analyze the information after receiving it. In this part of the project, a web application was developed to process the transmitted data and then store it in a database and finally convert the stored information to visible to users. This allows you to see the speed, direction of movement, and the object's locations on the map. Furthermore, a heatmap was implemented to show the frequently visited places by users.
\end{abstract} 