\chapter{Future Work}
The GPS antenna has a relatively high power consumption. There are two proposed ways to reduce power consumption in this system. The first way that can be suggested for this system is to use machine learning algorithms to predict the object's next move. Another way is using LoRaWAN protocol instead of GPS to locate the object.

Another thing that can be done is to add sensors and actuators to this system. For example, an accelerometer sensor can be used to monitor the object's movement, and only when it is moving, GPS information is sent to the server, which will reduce power consumption. \\
A camera can also be installed on the designed system. Consequently, in addition to the information sent through GPS, we can also use this camera's images to monitor the location.

As we have said, one of the features of this system was receiving the position of the person by sending a message to the SIM card number inserted in this system. Despite its advantages, it can create security risks for people. Therefore, it is possible to improve the security of the desired tracking system and specify that if it receives a message from a specified and predetermined number, it will send the person's location. Otherwise, no information will be exchanged.

This system is designed in such a way that it can be customized for different applications. For example, we can specify the permissible range for the movement of the object. Therefore, if the object leaves the specified range, the system will automatically contact institutions such as police and minimize human errors.