\cleardoublepage
%\pagebreak
\phantomsection
\addcontentsline{toc}{chapter}{References}
\begin{thebibliography}{99}
	
	\bibitem{1}M. Mukhtar, "\textit{{GPS} based Advanced Vehicle Tracking and Vehicle Control System,}" International Journal of Intelligent Systems and Applications, Feb. 2015.
	
	\bibitem{2}S. Hussain Shah and I. Yaqoob, "\textit{A survey: Internet of Things ({IOT}) technologies,  applications and challenges,}" 2016 {IEEE} Smart Energy Grid Engineering ({SEGE}), Aug. 2016.
	
	
	\bibitem{3}Md. Rahman, J.Mou, K. Tara and Md. Sarkar, "\textit{Real time Google map and Arduino based vehicle tracking system,}" 2016 {IEEE} Smart Energy Grid Engineering ({SEGE}), Aug. 2016.
	
	
	\bibitem{4}J. Saranya and J. Selvakumar, "\textit{Implementation of children tracking system on android mobile terminals,}" Implementation of children tracking system on android mobile terminals, Apr. 2013.
	
	\bibitem{5}B. Bidabad and A. Tayebi, "\textit{Design and implementation of vehicle tracking system using GPS/GSM/GPRS technology and smartphone application,}" 2014.
	
	\bibitem{6}M. Omar, H. Rashaand and T. Nicolae, "\textit{Design and implementation of real time tracking system based on Arduino Intel Galileo,}" 2016 8th International Conference on Electronics,  Computers and Artificial Intelligence ({ECAI}), Jun. 2016.

	\bibitem{7}T. Agrawal and M. Qadeer, "\textit{Tracing Path with Arduino Uno using {GPS} and {GPRS}/{GSM},}" 2018 International Conference on Computing,  Power and Communication Technologies ({GUCON}), Sep. 2018.
	
	
	
	
\end{thebibliography}